From Causal Discovery to Intervention Simulation: Modeling Precariousness and Depression in the HELIUS Study

### 2025-06-24 draft_v1/draft_v2.tex
add linear model

\includegraphics[width=0.9\textwidth,height=\textheight]{draft_v1_files/figure-pdf/fig-dist-1.pdf}

@@

\begin{center}
\includegraphics{draft_v1_files/figure-pdf/unnamed-chunk-12-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.55\textwidth,height=\textheight]{draft_v1_files/figure-pdf/unnamed-chunk-13-1.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.7\textwidth,height=\textheight]{draft_v1_files/figure-pdf/unnamed-chunk-14-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.7\textwidth,height=\textheight]{draft_v1_files/figure-pdf/unnamed-chunk-15-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics{draft_v1_files/figure-pdf/unnamed-chunk-16-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.7\textwidth,height=\textheight]{draft_v1_files/figure-pdf/unnamed-chunk-17-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.7\textwidth,height=\textheight]{draft_v1_files/figure-pdf/unnamed-chunk-18-1.pdf}
\end{center}

@@

\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics{draft_v1_files/figure-pdf/unnamed-chunk-19-1.pdf}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics{draft_v1_files/figure-pdf/unnamed-chunk-19-2.pdf}
\end{center}
\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics{draft_v1_files/figure-pdf/unnamed-chunk-19-3.pdf}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics{draft_v1_files/figure-pdf/unnamed-chunk-19-4.pdf}
\end{center}
\end{minipage}%

@@

\begin{center}
\includegraphics[width=0.6\textwidth,height=\textheight]{draft_v1_files/figure-pdf/unnamed-chunk-20-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics{draft_v1_files/figure-pdf/unnamed-chunk-21-1.pdf}
\end{center}

\begin{center}
\includegraphics{draft_v1_files/figure-pdf/unnamed-chunk-22-1.pdf}
\end{center}

>>>>

\includegraphics[width=0.9\textwidth,height=\textheight]{draft_v2_files/figure-pdf/fig-dist-1.pdf}

@@

\begin{center}
\includegraphics{draft_v2_files/figure-pdf/unnamed-chunk-12-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.55\textwidth,height=\textheight]{draft_v2_files/figure-pdf/unnamed-chunk-13-1.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.7\textwidth,height=\textheight]{draft_v2_files/figure-pdf/unnamed-chunk-14-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.7\textwidth,height=\textheight]{draft_v2_files/figure-pdf/unnamed-chunk-15-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics{draft_v2_files/figure-pdf/unnamed-chunk-16-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.7\textwidth,height=\textheight]{draft_v2_files/figure-pdf/unnamed-chunk-17-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.7\textwidth,height=\textheight]{draft_v2_files/figure-pdf/unnamed-chunk-18-1.pdf}
\end{center}

@@

\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics{draft_v2_files/figure-pdf/unnamed-chunk-19-1.pdf}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics{draft_v2_files/figure-pdf/unnamed-chunk-19-2.pdf}
\end{center}
\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics{draft_v2_files/figure-pdf/unnamed-chunk-19-3.pdf}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics{draft_v2_files/figure-pdf/unnamed-chunk-19-4.pdf}
\end{center}
\end{minipage}%

@@

\begin{center}
\includegraphics[width=0.6\textwidth,height=\textheight]{draft_v2_files/figure-pdf/unnamed-chunk-20-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics{draft_v2_files/figure-pdf/unnamed-chunk-21-1.pdf}
\end{center}

\begin{center}
\includegraphics{draft_v2_files/figure-pdf/unnamed-chunk-22-1.pdf}
\end{center}
